---
title: "P8105_hw1_md3851"
author: "Misbath Daouda"
date: "9/13/2019"
output: github_document
---



## Problem 1
### Part 1: Creating a table 

```{r setup, include=FALSE}
library(tidyverse)
```

This chunck of code creates a table following the guidelines for problem 1.
```{r problem 1 part 1}
example_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("This", "is", "an", "assignment", "for", "data", "science", "class"),
  vec_factor = factor(c("small", "medium", "large", "small", "medium", "large", "small", "small"))
)
example_df
```

### Part 2: Understanding the nature of variables  
This chunck of code attempts to calculate the respective means of the variables included in the table from Part 1 
```{r problem 1 part 2, warning=FALSE}
mean(pull(example_df, var=norm_samp))
mean(pull(example_df, var=norm_samp_pos))
mean(pull(example_df, var=vec_char))
mean(pull(example_df, var=vec_factor))
```
R returns error messages along with the value "NA" for the character and factor variables (ie, vec_char and vec_factor). The mean can only be calculated for numeric and logical variables (ie, norm_samp and norm_samp_pos).

### Part 3: Converting variables 
```{r problem 1 part 3, results='hide', warning=FALSE}
as.numeric(pull(example_df, var=norm_samp_pos))
as.numeric(pull(example_df, var=vec_char))
as.numeric(pull(example_df, var=vec_factor))
```
The "as.numeric" function succesfully transforms the logical variable using a binary system to represent the TRUE/FALSE options. This explains what happened when taking the mean: R treated this logical variable as a numeric variable made up of two values (0 and 1). This is why the mean (0.25) falls between 0 and 1. 

The "as.numeric" function also succesfully assigns integers (ie, 1, 2, 3) to the three levels of the factor variable. However, the character variable cannot be converted to a numeric one. 

```{r problem 1 part 3 continued}
pull(
  example_df, var=norm_samp) * as.numeric(
  pull(example_df, var=norm_samp_pos)
  )
pull(
  example_df, var=norm_samp) * as.factor(
  pull(example_df, var=norm_samp_pos)
  )
pull(
  example_df, var=norm_samp) * as.numeric(
  as.factor(pull(example_df, var=norm_samp_pos))
  ) 
```

## Problem 2
This chunck of code creates a table following the guidelines for problem 2.
```{r}
example2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  sum_greater_one = x + y > 1,
  vec_num = as.numeric(sum_greater_one),
  vec_factor = as.factor(sum_greater_one)
)

example2_df
```

This data frame contains `r ncol(example2_df)` variables and 
`r nrow(example2_df)` observations. The mean and median of the sample are `r mean(pull(example2_df, x))` and `r median(pull(example2_df, x))` respectively. Its standard deviation is `r sd(pull(example2_df, x))`.

The proportion of the sample such that x + y > 1 is `r mean(pull(example2_df,vec_num))`.

```{r}
ggplot(example2_df, aes(x = x, y = y, color = sum_greater_one)) + geom_point()
ggplot(example2_df, aes(x = x, y = y, color = vec_num)) + geom_point()
ggplot(example2_df, aes(x = x, y = y, color = vec_factor)) + geom_point()

```






