---
title: "P8105_hw1_md3851"
author: "Misbath Daouda"
date: "9/13/2019"
output: github_document
---



## Problem 1
### Part 1: Creating a table 

This chunck of code creates a table following the guidelines for homework 1 
```{r problem 1, echo=FALSE}
library(tidyverse)
example_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("This", "is", "an", "assignment", "for", "data", "science", "class"),
  vec_factor = factor(c("small", "medium", "large", "small", "medium", "large", "small", "small"))
)
example_df
```

### Part 2: Understanding the nature of variables  
This chunck of code attempts to calculate the respective means of the variables included in the table from Part 1 
```{r}
mean(pull(example_df, var=norm_samp))
mean(pull(example_df, var=norm_samp_pos))
mean(pull(example_df, var=vec_char))
mean(pull(example_df, var=vec_factor))
```
This shows that the mean can only be calculated for numeric and logical variables (ie, norm_samp and norm_samp_pos)

### Part 3: Converting variables 
```{r problem 1 part 3, include=FALSE}
as.numeric(pull(example_df, var=norm_samp_pos))
as.numeric(pull(example_df, var=vec_char))
as.numeric(pull(example_df, var=vec_factor))
```
```{r}
pull(
  example_df, var=norm_samp) * as.numeric(
  pull(example_df, var=norm_samp_pos)
  )
pull(
  example_df, var=norm_samp) * as.factor(
  pull(example_df, var=norm_samp_pos)
  )
pull(
  example_df, var=norm_samp) * as.numeric(
  as.factor(pull(example_df, var=norm_samp_pos))
  ) 
```

## Problem 2
example2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  sum_greater_one = x + y > 1,
  vec_num = as.numeric(sum_greater_one),
  vec_factor = as.factor(sum_greater_one)
)

example2_df

